---
title: "'didi' Package"
output: html_document
date: "2024-03-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This gives a basic example of how to use the 'Didi' estimator to visualise the impact of continuous covariates on time-to-event outcomes

## Install/load package
```{r load,message=F}
  library(devtools)
  devtools::install_github("richJJackson/didi")
  library(didi)
```

## Simulated data
Three covariates are required which are simulated for N=100 observations

* Time variable: using rexp(N,0.05)
* Censoring Indicator: using rbinom(N,1,0.1)
* Covariate: using rnorm(N)

```{r dataSim}
  N <- 100
  st <- rexp(N,0.05)
  cen <- rbinom(N,1,0.1)
  x <- rnorm(N)
```

## Figure

```{r didiPlot}
  didiPlot(st,cen,x)
```

## Details

Find code at: https://github.com/richJJackson/didi

## Reference

Jackson RJ, Cox TF. Kernel hazard estimation for visualisation of the effect of a continuous covariate on time‐to‐event endpoints. Pharmaceutical Statistics. 2022 May;21(3):514-24.
