---
title: "didi-vignette"
author: "Richard Jackson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{didi-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height= 5
)

library(didi)
library(survival)
library(reshape2)
library(ggplot2)
```

## Intro

This gives a basic example of how to use the 'Didi' estimator to visualise the impact of continuous covariates on time-to-event outcomes

## Simulated data
Three covariates are required which are simulated for N=500 observations using 
rnorm(N, 8,2).  We then generate a hazard parameter based on a the following sigmoid formula:

h = 0.04 + 1/(6+exp(-a(x-b)))

with parametes a=2 and b=9 used.  Based on this we generate survival time data
from an exponential distribution with hazard parameter h.  A basic censoring
indicator is generated using 'rbinom(N,1,0.7)`


```{r dataSim}
  set.seed(041084)
  N <- 500
  x <- rnorm(N,8,2)
  
  a <- 2
  b <- 9
  lam <- 0.04 + 1/(6+exp(-a*(x-b)))
  st <- rexp(N,lam)
  cen <- rbinom(N,1,0.55)

  plot(x,lam,main="plot of simulated realtionship between a covariate (x)
         and the hazard rate parameter")
```

## Calculate the double weighted kernel (Didi) estimator


```{r didiPlot, echo=FALSE}
didi <- didiEst(st,cen,x,bw.x=0.75,bw=1)
```


```{r}
plot(didi)
```


## Example

To get an idea of how this compares to a standard Kaplan Meir plot we can 
dichotomise 'x'

```{r}

xn <- cut(x,c(0,8,Inf),c("low","high"));table(xn)
sfit <- survfit(Surv(st,cen)~xn)
plot(sfit,col=c(2,4),lwd=4)
```


## Details

Find code at: https://github.com/richJJackson/didi

## Reference

Jackson RJ, Cox TF. Kernel hazard estimation for visualisation of the effect of a continuous covariate on time‐to‐event endpoints. Pharmaceutical Statistics. 2022 May;21(3):514-24.



